Photographic Text-to-Image Synthesis \\ with a Hierarchically-nested Adversarial Network

### 2017-11-13 cvpr2018.tex

\usepackage{float}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage{capt-of}% or \usepackage{caption}
\usepackage{booktabs}
\usepackage{varwidth}
\usepackage{wrapfig}
\usepackage{makecell}

@@

\begin{figure*}[t]
	\centering
	\includegraphics[width=0.95\textwidth]{figure/views2.pdf}
	\vspace{-.2cm}
	\caption{Overviews of some typical GAN frameworks. \textbf{A} uses multi-stage GANs \cite{han2017stackgan,denton2015deep}. \textbf{B} uses multiple discriminators with one generator \cite{durugkar2016generative,tu_etal_nips17_d2gan}. \textbf{C} progressively trains symmetric discriminators and generators \cite{Karras2017progressive,huang2016stacked}. \textbf{A} and \textbf{C} can be viewed as decomposing high-resolution tasks to multi-stage low-to-high resolution tasks.  \textbf{D} is our proposed framework that uses a single-stream generator with hierarchically-nested discriminators trained end-to-end.} \label{fig:archs-review}
\end{figure*}

@@

\subsection{Adversarial objective basics}
In brief, the two-player game in GANs \cite{goodfellow2014generative} is played by a generator $G$ network and a discriminator $D$ network, which are alternatively trained to compete with each other and thereby improve each other. The discriminator is optimized to distinguish synthesized images from real images, meanwhile, the generator is trained to generate realistic images to fool the discriminator. Concretely, the overall min-max optimization objective is defined as: 
%where the optimal $G$ and $D$ can be obtained by 
%The discriminator is optimized to distinguish synthesized images from real images, meanwhile, the generator is trained to fool the discriminator and transform an input distribution $p_z$ to the true data distribution $p_{data}$. Concretely, the overall training procedure can be analogous to the following two-player min-max game $\mathcal{L}(D, G)$, where the optimal $G$ and $D$ can be obtained by 
\begin{equation}
\label{equ:GAN}
\begin{split}
G^*, D^* = \arg~\underset{G}{\min}\ \underset{D}{\max}~ \mathcal{L}(D, G, Y, \bm z)
\end{split}
\end{equation}
\textcolor{red}{where $Y$ denotes training images and $\bm z\sim\mathcal{N}(0,1)$ denotes a random noise. The loss $\mathcal{L}$ aims to minimize the Jensen-Shannon divergence between the data and model distributions. }

@@

\subsection{Hierarchical-nested adversarial objectives}
%Directly predicting high resolution synthesized images are challenging, not only because of the difficulties in training but also due to the large variation and instability in the hidden layers.
Numerous methods have demonstrated ways to unite generators and discriminators for image synthesis. Figure \ref{fig:archs-review} and Section 2 discuss some typical frameworks.
Our method actually explores a new dimension of playing this adversarial game along the depth of a CNN (Figure \ref{fig:archs-review} D), which integrates additional discriminators at mid-level features of the generator $\mathcal{G}$. 
The hierarchically-nested objectives 
%We conjecture that adding hierarchical adversarial objective using side outputs can
act as regularizers to the hidden space of $\mathcal{G}$, which can reduce the training instability and also offer a short path for better error signals.

@@

%This architecture resemble the proposed inverse architectures in edge detection\cite{xie2015holistically} and classification \cite{lee2015deeply}, which demonstrate that additional supervision to hidden layers can improve model generalization and boost optimization.  
\begin{equation}
\label{side}
X_1,..., X_s = \mathcal{G}(\bm t, \bm z), 
\end{equation}
where  $\bm t\sim p(data)$ denotes a sentence embedding vector in the real training data distribution (generated by a text character encoder). $\mathcal{G}$ produces $s-1$ side outputs (size-growing images) and a final output $X_s$ with the highest resolution.

@@

For each side output $X_i$, we propose to apply a discriminator $D_i$ to perform independently adversarial games. Therefore, our full min-max objective is defined as follows: 
\begin{equation}
\label{equ:optim}
\begin{split}
  \mathcal{G}^*, \mathcal{D}^*&  =  \arg~\underset{G}{\min}\ \underset{\mathcal{D}}{\max}~ \mathcal{L}(\mathcal{G},\mathcal{D}, \mathcal{Y}, \bm t, \bm z) \\
  \text{where} \;\;	 \mathcal{D} & \in  \{D_1, ..., D_s\}, \; \mathcal{Y} = \{Y_1, ..., Y_s\}
\end{split}
\end{equation}
where $ \mathcal{Y}$ denotes a set of training images at multi-scales, $\{1,...,s\}$.
%where $\mathcal{D}$ contains the optimal discriminators $\{D_1^*, ..., D_o^*\}$, and $ \mathcal{L}(G,\mathcal{D}, \bm{X}, \bm{T} )$ is the full objective of this mini-max game.
%Please note that in this setting, 
Compared with Eq. (\ref{equ:GAN}), one generator competes with multiple discriminators at different hierarchies (Figure \ref{fig:archs-review} D). 
\textcolor{red}{Discriminators do not share weights with each other, which offers them full flexibility to focus on learning diverse discriminative features in different contextual scales.
In principle, the lower-resolution side output is forced to learn semantic consistent image structures (e.g., object sketch, color, and background), and the subsequent higher-resolution side outputs are used to render details to the images. 
Since the model is trained in an end-to-end fashion, we can obtain more consistent information exhibited in both lower and higher-resolution outputs compared with StackGAN. More results can be founded in experiments. 
According to this goal, we present the following adversarial losses to support more effective multi-purpose discriminators.}

@@

\textbf{Visual-semantic similarity~}
\textcolor{red}{Since the aforementioned evaluation methods can not measure alignment between the generated images and the text description, we introduce a new qualitative measurement, namely visual-semantic similarity (VS similarity) inspired by \cite{vsemb}.} Denote $\bm{v}$ as the feature vector extract by a pre-trained CNN model $f_{cnn}$ (Inception-v2 \cite{inception} pre-trained on Imagenet), and $\bm{t}$ denote the text embedding. 
We define a scoring function $s(\bm{x}, \bm{y})=\frac{\bm{x}\cdot \bm{y}}{||\bm{x}||\cdot ||\bm{y}||}$. 
We learn two mapping functions $f_v$ and $f_t$, which map both image and sentence embeddings into one semantic space $\mathbb{R}^{512}$, by minimizing the following bi-directional ranking loss:
\begin{equation}
\begin{split}
\mathcal{L}_{vs} &= \sum_{ \bm{v} }\sum_{ \bm{t^-} }~\max( 0, \delta- s(f_v(\bm{v}), f_t( \bm{t^-} ))) \\
&+ \sum_{ \bm{t} }\sum_{ \bm{v-} }~\max( 0,  \delta- s(f_t(\bm{t}), f_v( \bm{v^-} )))
\end{split}
\end{equation}
where $\delta$ is the margin, which is set as 0.2, every $(\bm{v}, \bm{t})$ is a ground truth image text pair, $\bm{t^-}$ denotes a mismatching text description for the image corresponding to $\bm{v}$, and vice-versa for $\bm{v^-}$. In the testing stage, given an text embedding $\bm{t}$, and the generated images $o$, the corresponding vs-similarity will be calculated as $s(f_{cnn}(o), \bm{t})$. Higher score indicates semantic consistency.

@@

\begin{figure*}[t]
	\centering
	\includegraphics[width=0.99\textwidth]{figure/cub.pdf}
	\vspace{-.2cm}
	\caption{The generated images on CUB compared with StackGAN. Each sample shows the input text and generated $64^2$ (left) and $256^2$ (right) images. Our results have significantly higher quality and preserve more semantic details, for example, ``the brown and white feathers and read head'' in the last column is much better reflected in our images. Moreover, we observed our birds have more diverse poses (e.g. the frontal view in the the second and the back view forth columns).}
	\vspace{-0.2cm}
	\label{fig:vis-cub}
\end{figure*}
\begin{figure*}[t]
	\centering
	\includegraphics[width=0.99\textwidth]{figure/flowers.pdf}
	\vspace{-.2cm}
	\caption{The generated images on Oxford compared with StackGAN. Each sample shows the input text and generated $64^2$ (left) and $256^2$ (right) images. Our generated images perform more natural satisfiability and higher contrast.} \label{fig:vis-oxford}
	\vspace{-.2cm}
\end{figure*}

\begin{table}[t] % retrieval
	\small
	\begin{center}
		\begin{tabularx}{.435\textwidth}{c|ccc}
			\specialrule{1.5pt}{0pt}{0pt}  
			\multirow{2}{*}{Method}	& \multicolumn{3}{c}{Dataset}	\\ \cline{2-4}
			&	 CUB		&	Oxford  & COCO		     \\ \hline
			StackGAN     &	$.228{\pm}.162$	&	 $.278{\pm}.134$			&  $-{\pm}-$		\\

			Ground Truth	&	${.302{\pm}.151}$	&	$ {.336{\pm}.138}$			&  -  \\ \hline
			HDGAN 		&	$\bm{.246{\pm}.157}$	&	$ \bm{.296{\pm}.131}$			&  -  \\ \hline
		\end{tabularx} 
	\end{center}
	\vspace{-.4cm}
	\caption{The VS similarity evaluation on three datasets. The higher score represents higher semantic consistency between the generated images and the text information. } \label{table:vss}
\end{table}

@@

\begin{figure*}[t]
	%	\begin{center}
	\centering
	\begin{subfigure}[t]{0.69\textwidth}
		%	\centering
		\includegraphics[width=0.99\textwidth]{figure/multisample_cub.pdf}
	\end{subfigure} 
	\begin{subfigure}[t]{0.3\textwidth}
		%	\centering
		\includegraphics[width=0.99\textwidth]{figure/cub_multires.pdf}
	\end{subfigure}
	\vspace{-.2cm}
	\caption{Left: Diversity test given a single input text. HDGAN (top) show obviously more details and higher diversity. Right: Side outputs of HDGAN with increasing resolutions. Different resolutions are semantically consistent and semantic details emerges as resolution increases.  \label{fig:multiple-test}} 	\vspace{-.3cm}
	%\end{center}
\end{figure*}

\begin{table}[t] % retrieval
	\begin{minipage}[b]{0.50\linewidth}
		%\centering
		\includegraphics[width=0.99\textwidth,height=0.7\textwidth]{figure/ms_ssmi.pdf}
		\vspace{-1.8cm}
	\end{minipage} %\hfill
	\begin{minipage}[b]{0.49\linewidth}
		\begin{tabularx}{.9\textwidth}{c|c}
			\specialrule{1.5pt}{0pt}{0pt}  
			Method   &  MS-SSMI \\ \hline
			StackGAN &   0.234   \\ 
			Prog.GAN &   0.225    \\ \hline
			HDGAN    &   \textbf{0.215}    \\ \hline
		\end{tabularx}
	\end{minipage}
	\vspace{0.2cm}
	\caption{Left: Class-wise MS-SSMI evaluation. Lower score indicates higher intraclass invariance. The points below the equality line represent classes our HDGAN wins. Right: Overall (no class-wise) score evaluation.} \label{fig:msssmi}
	\vspace{-0.4cm}
\end{table}

Table \ref{fig:msssmi} shows the MS-SSMI image quality evaluation score compared with StackGAN and Prog.GAN on CUB. StackGAN and our HDGAN use the semantic text as input so the generated images retain class information. We compare the score with StackGAN. We randomly sample ${~}20,000$ image pairs (400 per class) and show the class-wise score in the left figure. HDGAN wins in majority of classes and also has lower inter-class standard deviation ($.023$ vs. $.032$).
Prog.GAN takes noises rather than text. Since MS-SSMI evaluates the image quality without text or class involvement, we can compare with it. Following the procedure of Prog.GAN, we randomly sample ${~}10,000$ image pairs for each comparing method (For Prog.GAN, we use generated $256^2$ images provided by the author) and show the results in the right table. Our method outperforms both StackGAN and Prog.GAN.

\begingroup
\setlength{\intextsep}{-4pt}%
\setlength{\columnsep}{0pt}%
\begin{wrapfigure}{r}{0.24\textwidth}
	\centering
	\includegraphics[width=0.245\textwidth]{figure/multiscale_inception.pdf}
	\vspace{-12pt}
\end{wrapfigure}
%Table \ref{table:multiscales}
The right figure compares the the multi-resolution inception score on CUB. Our results are from the side outputs of a single model. As can be observed, our $64^2$ images outperforms $128^2$ images of StackGAN and our $128^2$ images outperforms $256^2$ images of StackGAN substantially. It strongly demonstrates our HDGAN better preserves semantically consistent information in all resolutions. Figure \ref{fig:multiple-test} qualitatively validate this property.

\begin{figure}[t]
	\centering
	\includegraphics[width=0.48\textwidth]{figure/interp.pdf}
	\vspace{-.5cm}
	\caption{Text embedding interpolation from the source to target sentence results in smooth image changes approaching the targeting sentence. } \label{fig:interp}
	\vspace{-.3cm}
\end{figure}
\subsubsection{Style Transfer Using Sentence Interpolation}

\textcolor{red}{Ideally, a well trained model should learn a smooth linear latent manifold of the images. To demonstrate our model's generalization capability, we generate images using the linearly interpolated embeddings between two source sentences. During this experiment, we fix the all the random noises to make the object and background consistent. As is shown in Figure~\ref{fig:interp}, the generated images show gradual and smooth changes reflecting the semantic changing in sentences, while still maintaining plausible object pose and shape. In the first row, the generated birds gradually turn the color from yellow to brown. In the second row, more complicated sentences containing more detailed appearance information (e.g., blue peaks, and yellow wing) are used, we can see that our model is still be able to successfully capture these subtle information and tune the bird appearance gradually. }

@@

\section{On the effects of Individual Components}
\subsection{Hierarchically-nested adversarial training}
Our hierarchically-nested adversarial discriminators a role of regularizing the layer representations (at scale $\{64, 128, 256\}$). 
%Our full method applies it on feature maps at $\{64, 128, 256\}$. 
In Table \ref{tab:ablation} right, we compare the results by removing part of discriminators. 
As can be seen, increasing the usage of discriminators at different scales have positive effectives. And using discriminators on $64^2$ is critical (by comparing 64-256 and 128-256 cases). For now, we are unsure if adding more discriminators and adding on lower resolution would be helpful. Further investigation will be conducted to validate it.
StackGAN emphasizes the importance of using text embeddings with mid-level features of the $256^2$ generator by showing an large drop from $3.7$ to $3.45$ without doing so, which helps maintains the diversity and semantic consistency. While in our method, we only use text embeddings at the input. Our significantly improved results demonstrate that effectiveness of the hierarchically-nested adversarial training to achieve this goal.

@@

\begin{table}[t] % retrieval
	\small
	\begin{minipage}[b]{0.5\linewidth}
			\begin{tabularx}{.98\textwidth}{c@{\hskip1pt}|c@{\hskip1pt}c@{\hskip1pt}}
				\specialrule{1.5pt}{0pt}{0pt}  
				Metric 			&   VS 	 & MS-SSMI   	\\  \hline
				w/o Img         &   $.25{\pm}.16$      &   $.215$           \\  \hline
				w/ global       &   $-$      &   $-$           \\ \hline
				w/local         &   $-$ 	 &   $-$		    \\ \hline
			\end{tabularx}
		\vspace{-0.8cm}
	\end{minipage} %\hfill
	\begin{minipage}[b]{0.49\linewidth}
		\begin{tabularx}{.98\textwidth}{ccc|c}
			\specialrule{1.5pt}{0pt}{0pt}  
			\multicolumn{3}{c|}{Components}	&  \multirow{2}{*}{\thead{Inception \\ score}}	\\ \cline{1-3}
			64	& 128	& 256 			& 		\\ \hline
			&  		&	\checkmark	&	${3.52{\pm}.04}$	\\ 
			&  	\checkmark	&	\checkmark	&	${3.99{\pm}.04}$	\\
			\checkmark	&  			&	\checkmark	&  ${4.14{\pm}.03}$		\\
			\checkmark	&  \checkmark		&	\checkmark	&	${4.15{\pm}.05}$ \\ \hline

		\end{tabularx}
	\end{minipage}
	\vspace{-0.2cm}
	\caption{Ablation study on the local adversarial loss (left table) and hierarchically-nested adversarial learning (right table). See text for detailed explanation.} \label{tab:ablation}
\end{table}

\subsection{Design principles}
%Note that for text-to-image synthesis, StackGAN is the only successful method to generate $256{\times}256$ images.
StackGAN shows the difficulty of directly training a vanilla $256{\times}256$ GAN to generate meaningful images. 
We test this extreme case using our method by removing all nested intermediate discriminators (the first row of Table \ref{tab:ablation} left). Our method still generates fairly good results. 
%Figure \ref{fig:vallina-res} shows the qualitatively results. 
Based on our experience, the success is because of our effective generator designs that helps gradient flows.

Initially, we tried to share top layers of the hierarchical discriminators of HDGAN inspired by \cite{liu2017unsupervised} with an intuition to reduce their variances and unify their common goal (i.e. differentiates real and fake despite difficult scales). However, we did not find benefits from this mechanism and our independent discriminators can be trained very stably.

@@

\section{Conclusion}
In this paper, we present a novel, effective, and end-to-end method to tackle the problem of generating high resolution images using text description. We introduce the hierarchical-nested adversarial discriminators to help generator training. To improve the model's capability to render fine-grained local details, we propose a hierarchal local image loss to emphasize local patch realism. We also introduce a new evaluation metric for text-to-image synthesis to evaluate the semantic consistency between generated images and conditioned text.
Extensive experiment results demonstrate that our method, namely HDGAN, performs significantly better than existing state of the arts.

{\small
\bibliographystyle{ieee}
\bibliography{reference_zizhao,egbib}
}

>>>>

\usepackage{float}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage{capt-of}% or \usepackage{caption}
\usepackage{booktabs}
\usepackage{varwidth}
\usepackage{wrapfig}

@@

\begin{figure*}[t]
	\centering
	\includegraphics[width=0.95\textwidth]{figure/views2.pdf}
	\vspace{-.2cm}
	\caption{Overviews of some typical GAN frameworks. \textbf{A} decomposes tasks multi-stage GANs \cite{han2017stackgan,denton2015deep}. \textbf{B} uses multiple discriminators with one generator \cite{durugkar2016generative,tu_etal_nips17_d2gan}. \textbf{C} progressively trains symmetric discriminators and generators \cite{Karras2017progressive,huang2016stacked}. \textbf{A} and \textbf{C} can be viewed as decomposing high-resolution tasks to multi-stage low-to-high resolution tasks.  \textbf{D} is our proposed framework that uses a single-stream generator with hierarchically-nested discriminators trained end-to-end.} \label{fig:archs-review}
\end{figure*}

@@

\subsection{Adversarial objective basics}
In brief, the two-player game in GANs \cite{goodfellow2014generative} is played by a generator $G$ network and a discriminator $D$ network, which are alternatively trained to compete with each other and thereby improve each other. The discriminator is optimized to distinguish synthesized images from real images, meanwhile, the generator is trained to generate realistic images to fool the discriminator. Concretely, the overall min-max optimization objective is defined as: 
%where the optimal $G$ and $D$ can be obtained by 
%The discriminator is optimized to distinguish synthesized images from real images, meanwhile, the generator is trained to fool the discriminator and transform an input distribution $p_z$ to the true data distribution $p_{data}$. Concretely, the overall training procedure can be analogous to the following two-player min-max game $\mathcal{L}(D, G)$, where the optimal $G$ and $D$ can be obtained by 
\begin{equation}
\label{equ:GAN}
\begin{split}
G^*, D^* = \arg~\underset{G}{\min}\ \underset{D}{\max}~ \mathcal{L}(D, G)
\end{split}
\end{equation}
\textcolor{red}{where the loss $\mathcal{L}$ aims to minimize the Jensen-Shannon divergence between the data and model distributions. }

@@

\subsection{Hierarchical-nested adversarial objectives}
%Directly predicting high resolution synthesized images are challenging, not only because of the difficulties in training but also due to the large variation and instability in the hidden layers.
Numerous methods have demonstrated a variety of ways to build GANs for image synthesis. Figure \ref{fig:archs-review} and Section 2 discuss some typical frameworks.
Our method explores a new dimension of playing this adversarial game along the depth of a CNN (Figure \ref{fig:archs-review} D), which integrates additional discriminators at mid-level features of the generator $\mathcal{G}$. 
The hierarchically-nested objectives 
%We conjecture that adding hierarchical adversarial objective using side outputs can
act as regularizers to the hidden space of $\mathcal{G}$, which can reduce the training instability and also offer a short path for better error signals.

@@

%This architecture resemble the proposed inverse architectures in edge detection\cite{xie2015holistically} and classification \cite{lee2015deeply}, which demonstrate that additional supervision to hidden layers can improve model generalization and boost optimization.  
\begin{equation}
\label{side}
X_1,..., X_s = \mathcal{G}(\bm t, \bm z), 
\end{equation}
where $\bm z\sim\mathcal{N}(0,1)$ denotes a random noise and $\bm t\sim p(data)$ denotes a sentence embedding vector in the real training data distribution (generated by a text character encoder). $\mathcal{G}$ produces $s-1$ side outputs (size-growing images) and a final output $X_s$ with the highest resolution.

@@

For each side output $X_i$, we propose to apply a discriminator $D_i$ to perform independently adversarial games. Therefore, our full min-max objective can be defined as follows: 
\begin{equation}
\label{equ:optim}
\begin{split}
  \mathcal{G}^*, \mathcal{D}^*&  =  \arg~\underset{G}{\min}\ \underset{\mathcal{D}}{\max}~ \mathcal{L}(\mathcal{G},\mathcal{D}, \mathcal{Y}, \bm t, \bm z) \\
  \text{where} \;\;	 \mathcal{D} & \in  \{D_1, ..., D_s\}, \; \mathcal{Y} = \{Y_1, ..., Y_s\}
\end{split}
\end{equation}
where $ \mathcal{Y}$ denotes training images at multi-scales, $\{1,...,s\}$.
%where $\mathcal{D}$ contains the optimal discriminators $\{D_1^*, ..., D_o^*\}$, and $ \mathcal{L}(G,\mathcal{D}, \bm{X}, \bm{T} )$ is the full objective of this mini-max game.
%Please note that in this setting, 
Compared with Eq. (\ref{equ:GAN}), one generator competes with multiple discriminators at different hierarchies. 
\textcolor{red}{Discriminators do not share weights with each other, which offers them full flexibility to focus on learning diverse discriminative features in different contextual scales.
In principle, the lower-resolution side output is forced to learn semantic consistent image structures (e.g., object sketch, color, and background), and the subsequent higher-resolution side outputs are used to render details to the images. 
Since the model is trained in an end-to-end fashion, we can observe more consistent information exhibited in both lower and higher-resolution outputs than StackGAN \cite{han2017stackgan}. More results can be founded in experiments. 
According to this goal, we present the following adversarial losses to support more effective multi-purpose discriminators.}

@@

\textbf{Visual-semantic similarity~}
Since the aforementioned evaluation methods can not measure alignment between the generated images and the text description, we introduce a new qualitative measurement, namely visual-semantic similarity (VS similarity) \cite{vsemb}. Denote $\bm{v}$ as the feature vector extract by a pre-trained CNN model $f_{cnn}$ (inception v2\cite{inception} pre-trained on Imagenet), and $\bm{t}$ denote the text embedding. 
We define a scoring function $s(\bm{x}, \bm{y})=\frac{\bm{x}\cdot \bm{y}}{||\bm{x}||\cdot ||\bm{y}||}$. 
We learn two mapping functions $f_v$ and $f_t$, which map both image and sentence embeddings into one semantic space $\mathbb{R}^{512}$, by minimizing the following bi-directional ranking loss:
\begin{equation}
\begin{split}
\mathcal{L}_{vs} &= \sum_{ \bm{v} }\sum_{ \bm{t^-} }~\max( 0, \delta- s(f_v(\bm{v}), f_t( \bm{t^-} ))) \\
&+ \sum_{ \bm{t} }\sum_{ \bm{v-} }~\max( 0,  \delta- s(f_t(\bm{t}), f_v( \bm{v^-} )))
\end{split}
\end{equation}
where $\delta$ is the margin, which is set as 0.2, every $(\bm{v}, \bm{t})$ is a ground truth image text pair, $\bm{t^-}$ denotes a mismatching text description for the image corresponding to $\bm{v}$, and vice-versa for $\bm{v^-}$. In the testing stage, given an text embedding $\bm{t}$, and the generated images $o$, the corresponding vs-similarity will be calculated as $s(f_{cnn}(o), \bm{t})$.

@@

\begin{figure*}[t]
	\centering
	\includegraphics[width=0.99\textwidth]{figure/cub.pdf}
	\vspace{-.2cm}
	\caption{The generated images on CUB compared with StackGAN. Each sample shows the input text and generated $64^2$ (left) and $256^2$ (right) images. Our results have significantly higher quality and preserve more semantic details, for example, ``the brown and white feathers and read head'' in the last column is much better reflected in our images. Moreover, we observed our birds have more diverse poses (e.g. the frontal view in the the second and the back view forth columns).}
	\vspace{-0.2cm}
	\label{fig:vis-cub}
\end{figure*}
\begin{figure*}[t]
	\centering
	\includegraphics[width=0.99\textwidth]{figure/flowers.pdf}
	\vspace{-.2cm}
	\caption{The generated images on Oxford compared with StackGAN (second row). Our generated images perform more natural satisfiability and higher contrast.} \label{fig:vis-oxford}
	\vspace{-.2cm}
\end{figure*}

\begin{table}[t] % retrieval
	\small
	\begin{center}
		\begin{tabularx}{.47\textwidth}{c|ccc}
			\specialrule{1.5pt}{0pt}{0pt}  
			\multirow{2}{*}{Method}	& \multicolumn{3}{c}{Dataset}	\\ \cline{2-4}
			&	 CUB		&	Oxford  & COCO		     \\ \hline
			StackGAN     &	$.228{\pm}.162$	&	 $.278{\pm}.134$			&  $-{\pm}-$		\\

			Ground Truth	&	${.302{\pm}.151}$	&	$ {.336{\pm}.138}$			& $.426{\pm}.157$  \\ \hline
			HDGAN 		&	$\bm{.246{\pm}.157}$	&	$ \bm{.296{\pm}.131}$ & $\bm{.178{\pm}.181}$  \\ \hline
		\end{tabularx} 
	\end{center}
	\vspace{-.4cm}
	\caption{The VS similarity evaluation on three datasets. The higher score represents higher semantic consistency between the generated images and the text information. } \label{table:vss}
\end{table}

@@

\begin{figure*}[t]
	%	\begin{center}
	\centering
	\begin{subfigure}[t]{0.69\textwidth}
		%	\centering
		\includegraphics[width=0.99\textwidth]{figure/multisample_cub.pdf}
	\end{subfigure} 
	\begin{subfigure}[t]{0.3\textwidth}
		%	\centering
		\includegraphics[width=0.99\textwidth]{figure/cub_multires.pdf}
	\end{subfigure}
	\vspace{-.2cm}
	\caption{Left: Diversity test given a single input text. Our results show obviously more details and higher diversity. Right: Side outputs of HDGAN with increasing resolutions. Different resolutions are fairly semantically consistent.  \label{fig:multiple-test}} 	\vspace{-.3cm}
	%\end{center}
\end{figure*}

\begin{table}[t] % retrieval
	\begin{minipage}[b]{0.50\linewidth}
		%\centering
		\includegraphics[width=0.99\textwidth,height=0.7\textwidth]{figure/ms_ssmi.pdf}
		\vspace{-1.8cm}
	\end{minipage} %\hfill
	\begin{minipage}[b]{0.49\linewidth}
		\begin{tabularx}{.9\textwidth}{c|c}
			\specialrule{1.5pt}{0pt}{0pt}  
			Method   &  MS-SSMI \\ \hline
			StackGAN &   0.234   \\ 
			Prog.GAN &   0.225    \\ \hline
			HDGAN    &   \textbf{0.215}    \\ \hline
		\end{tabularx}
	\end{minipage}
	\vspace{0.2cm}
	\caption{Left: Class-wise MS-SSMI evaluation. Lower score indicates higher intraclass invariance. The points below the equality line represent classes our HDGAN wins. Right: Overall (no class-wise) score evaluation.} \label{fig:msssmi}
	\vspace{-0.4cm}
\end{table}
\begin{figure}[t]
	\centering
	\includegraphics[width=0.48\textwidth]{figure/interp.pdf}
	\caption{Text interpolation visualization. } \label{fig:interp}
\end{figure}
Table \ref{fig:msssmi} shows the MS-SSMI image quality evaluation score compared with StackGAN and Prog.GAN on CUB. StackGAN and our HDGAN use the semantic text as input so the generated images retain class information. We compare the score with StackGAN. We randomly sample ${~}20,000$ image pairs (400 per class) and show the class-wise score in the left figure. HDGAN wins in majority of classes and also has lower inter-class standard deviation ($.023$ vs. $.032$).
Prog.GAN takes noises rather than text. Since MS-SSMI evaluates the image quality without text or class involvement, we can compare with it. Following the procedure of Prog.GAN, we randomly sample ${~}10,000$ image pairs for each comparing method (For Prog.GAN, we use generated $256^2$ images provided by the author) and show the results in the right table. Our method outperforms both StackGAN and Prog.GAN.

\begingroup
\setlength{\intextsep}{-4pt}%
\setlength{\columnsep}{0pt}%
\begin{wrapfigure}{r}{0.24\textwidth}
	\centering
	\includegraphics[width=0.245\textwidth]{figure/multiscale_inception.pdf}
	\vspace{-12pt}
\end{wrapfigure}
%Table \ref{table:multiscales}
The right figure compares the the multi-resolution inception score on CUB. Our results are from the side outputs of a single model. As can be observed, our $64^2$ images outperforms $128^2$ images of StackGAN and our $128^2$ images outperforms $256^2$ images of StackGAN substantially. It strongly demonstrates our HDGAN better preserves semantically consistent information in all resolutions. Figure \ref{fig:multiple-test} right shows some testing samples.

\subsubsection{Style Transfer Using Sentence Interpolation}

Ideally, a trained model should learn a smooth linear latent manifold of the images. To demonstrate our model's generalization capability, we generate images using the linearly interpolated  embedding using two source sentences. During this experiment, we fix the all the random noises to make the object and background consistent. As is shown in Figure~\ref{fig:interp}, the generated images show gradual and smooth changes reflecting the semantic changing in sentences, while still maintaining plausible object pose and shape. In the first row, the generated birds gradually turn the color from yellow to red, in the second row, more complicated sentences containing more detailed appearance information (e.g., blue peaks, and yellow wing) are used, we can see that our model is still be able to successfully capture these subtle information and tune the bird appearance gradually.

\textcolor{red}{We also evaluate some sentences that generated by ourself, the resulting images are shown in Figure~\ref{}, as we can see, our model are robust and generalize well to human descriptions that never seen before.}

@@

\section{On the effects of Individual Components}
\subsection{Hierarchically-nested adversarial training}
Our hierarchically-nested adversarial discriminators a role of regularizing the layer representations (at scale $\{64, 128, 256\}$). 
%Our full method applies it on feature maps at $\{64, 128, 256\}$. 
In Table \ref{table:deep-nest}, we compare the results by removing part of discriminators. The number of 
StackGAN emphasizes the importance of using text embeddings with mid-level features of the $256^2$ generator by showing an large drop from $3.7$ to $3.45$ without doing so, which helps maintains the diversity and semantic consistency. While in our method, we only use text embeddings at the input. Our significantly improved results demonstrate that effectiveness of the hierarchically-nested adversarial training to achieve this goal.

@@

\begin{table}[t] % retrieval
	\small
	\begin{minipage}[b]{0.5\linewidth}
			\begin{tabularx}{.98\textwidth}{c@{\hskip1pt}|c@{\hskip1pt}c@{\hskip1pt}}
				\specialrule{1.5pt}{0pt}{0pt}  
				Metric 			&   VS 	 & MS-SSMI   	\\  \hline
				w/o Img         &   $.25{\pm}.16$      &   $.215$           \\  \hline
				w/ global       &   $-$      &   $-$           \\ \hline
				w/local         &   $-$ 	 &   $-$		    \\ \hline
			\end{tabularx}
		\vspace{-0.8cm}
	\end{minipage} %\hfill
	\begin{minipage}[b]{0.49\linewidth}
		\begin{tabularx}{.96\textwidth}{ccc|c}
			\specialrule{1.5pt}{0pt}{0pt}  
			\multicolumn{3}{c|}{Components}	&  \multirow{2}{*}{Score}	\\ \cline{1-3}
			64	& 128	& 256 			& 		\\ \hline
			&  		&	\checkmark	&	${3.52{\pm}.04}$	\\ 
			&  	\checkmark	&	\checkmark	&	${3.99{\pm}.04}$	\\
			\checkmark	&  			&	\checkmark	&  ${4.14{\pm}.03}$		\\
			\checkmark	&  \checkmark		&	\checkmark	&	${4.15{\pm}.05}$ \\ \hline

		\end{tabularx}
	\end{minipage}
	\vspace{-0.2cm}
	\caption{Ablation study on the local adversarial loss (left) and hierarchically-nested adversarial learning (right). See text for details. See text for details.} \label{fig:ablation}
\end{table}

\subsection{Design principles}
%Note that for text-to-image synthesis, StackGAN is the only successful method to generate $256{\times}256$ images.
StackGAN shows the difficulty of directly training a vanilla $256{\times}256$ GAN to generate meaningful images. 
We test this extreme case using our method by removing all nested intermediate discriminators (the first row of Table \ref{table:deep-nest}). Our method still generates fairly good results. Figure \ref{fig:vallina-res} shows the qualitatively results. 
Based on our experience, the success is because of our framework designs in generators.

Initially, we tried to share top layers of the hierarchical discriminators of HDGAN inspired by \cite{liu2017unsupervised} with an intuition to reduce their variances and unify their common goal (i.e. differentiates real and fake despite difficult scales). However, we did not find any benefits from this and our independent discriminators can be trained very stably.

@@

\section{Conclusion}
In this paper, we present a novel and effective method to tackle the problem of generating high resolution images using text description. We introduce the hierarchical nested side outputs for deeply supervising the GAN training. To improve the model's capability to render fine-grained local details, we propose a hierarchal local image loss to boost the training. We also introduce a newly evaluation method for conditional gan, which leverage visual semantic embedding to judge the matching between generated images and provided text description, thus remove the necessary for human evaluation.
Extensive experiment results demonstrate that our method work significantly better than existing state of the arts.
{\small
\bibliographystyle{ieee}
\bibliography{reference_zizhao,egbib}
}
